Greenhouse gas emissions model - making scenarios

### 2021-11-11 Scenarios_report.Rmd
real farm scenarios

@@

GHG_simulation_scenarios<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                 scenarios = read.csv("data/scenarios.csv",fileEncoding="UTF-8-BOM"),
                                 model_function = ghg_emissions,
                                 functionSyntax = "plainNames")

>>>>

```{r}
scenarios<-read.table("data/scenarios.csv", sep = ",", fileEncoding = "UTF-8-BOM")

Kenyaherds<-read.table("data/Kenya_baseline_individual_cow_wNotes.csv", sep = ",",
                       fileEncoding = "UTF-8-BOM", header=TRUE)

scenarios<-data.frame(Variable=variables_to_update,param="both")

# count the number of animals for each type

animals<-table(Kenyaherds[,c("QQNO","animal_type")])

for(i in 1:nrow(animals))
  {coln<-paste0("Farm_",row.names(animals)[i])
   scenarios[,coln]<-NA
     scenarios[which(scenarios$Variable %in% paste0("N_animal_type_",1:12)),coln]<-animals[i,]
}

# for some animal-scale variables (e.g. milk yield), we need averages per farm

# farm-scale variables

Farms<-unique(Kenyaherds$QQNO)

for (f in Farms)
  {coln<-paste0("Farm_",f)
   scenarios[which(scenarios$Variable %in% "feeding_system"),coln]<-
     median(Kenyaherds[which(Kenyaherds$QQNO==f),"system"])
   }

write.csv(scenarios,"data/farm_scenarios.csv")

@@

GHG_simulation_scenarios<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                 scenarios = read.csv("data/farm_scenarios.csv",fileEncoding="UTF-8-BOM")[1:2,],
                                 model_function = ghg_emissions,numberOfModelRuns=10,
                                 functionSyntax = "plainNames")
